### 2012-12-10 trunk/htdocs/sigma.tex
Some colloid documentation
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1833 40876441-3496-0410-a613-a2fca35b2ae2

\begin{table}
\begin{center}
\begin{tabular}{llllllll}
\hline
Run & $-A, B$ & $\kappa$ & $\eta$ & $M$ & $\sigma$  & $L_0$ & $T_0$ \\
\hline
Run028 & 0.083 & 0.053 & 1.41 & 0.05  & 0.0625 & 31.8 & 718 \\
Run022 & 0.0625 & 0.04 & 0.5 & 0.25   & 0.0471 & 5.31 & 56.3 \\
Run029 & 0.0625 & 0.04 & 0.2 & 0.15   & 0.0471 & 0.849 & 3.61 \\
Run020 & 0.00625 & 0.004 & 0.025 & 2.00 & 0.00471 & 0.133 & 0.704 \\
Run030 & 0.00625 & 0.004 & 0.0065 & 1.25 & 0.00471 & 0.00829 & 0.0124 \\
Run019 & 0.003125 & 0.002 & 0.0014 & 4.00 & 0.00236 & 0.000831 & 0.000493 \\
Run032 & 0.00125  & 0.0008 & 0.0005 & 5.0 & 0.000943 & 0.000265 & 0.000141\\
\hline  
\end{tabular}
\end{center}
\caption{Table showing common parameter values following Kendon et al.
with the theoretical interfacial tension, $L_0$ and $T_0$. Note that
the order parameter mobility is used here (cf $\tilde{M} = 2M$) in
Kendon et al.}
\label{tab:r1}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{llllllll}
\hline
Run & $-A, B$ & $\kappa$ & $\eta$ & $M$ & $\sigma$  & $L_0$ & $T_0$ \\
\hline
Rks001 & 0.00625 & 0.004 & 1.41 & 0.05 & 0.0047 & 422 & 1.26e10$^5$\\
Rks002 & 0.00625 & 0.004 & 0.65 & 0.25 & 0.0047 & 89.7 & 1.24e10$^4$\\
Run028 & 0.083 & 0.053 & 1.41 & 0.05  & 0.0625 & 31.8 & 718 \\
Run022 & 0.0625 & 0.04 & 0.5 & 0.25   & 0.0471 & 5.31 & 56.3 \\
Run029 & 0.0625 & 0.04 & 0.2 & 0.15   & 0.0471 & 0.849 & 3.61 \\
Run020 & 0.00625 & 0.004 & 0.025 & 2.00 & 0.00471 & 0.133 & 0.704 \\
Run030 & 0.00625 & 0.004 & 0.0065 & 1.25 & 0.00471 & 0.00829 & 0.0124 \\
Run019 & 0.003125 & 0.002 & 0.0014 & 4.00 & 0.00236 & 0.000831 & 0.000493 \\
Run032 & 0.00125  & 0.0008 & 0.0005 & 5.0 & 0.000943 & 0.000265 & 0.000141\\
\hline  
\end{tabular}
\end{center}
\caption{Table showing common parameter values following Kendon et al.
with the theoretical interfacial tension, $L_0$ and $T_0$. Note that
the order parameter mobility is used here (cf $\tilde{M} = 2M$) in
Kendon et al. (KS values are extra sets used to low 1/$\dot{\gamma}T_0$.)}
\label{tab:r1}
\end{table}
